### 2024-03-22 src/analysis/regression_analysis.Rmd

# Let's run our analysis! 
## And see how genre prefferences as inferred from average ratings evolve over time

```{r libraries, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(fixest)
library(tidyr)
library(skimr)
library(infer)
library(modelsummary)
library(broom)
library(purrr)
library(viridis)
library(estimatr)
library(pdftools)
```

@@

## adding fixed effects
### titleType
We are observing behavior over time. But we are currently observing behavior for multiple types of behavior. Or more specifically, for both movies AND series. But these are two different things. So while we still want to know the general genre preference trends, we need to adjust for movie vs. series.

@@

If you compare these results against our skeleton model you may see that the standard errors have increased. This is good! this means our analysis has become a little more robust. But let's check our R-squared to be sure.

```{r echo=FALSE}
etable(simple_model)
```

```{r echo=FALSE}
etable(fixed_type_model)
```

@@

Last, because while out regression assumptions are mostly respected we still may want to increase the robustness of the coefficients. We do this by loosening these assumptions a little, given that heteroscedasticity appears to be a little shady we loosen that assumption a little and then check the R-squared again.

@@

etable(fixed_tth_model)
```

@@

```{r plotting results}

#make a plot that suits

>>>>

---
output:
  pdf_document: default
  html_document: default
---
# Let's run our analysis! 
## And see how genre prefferences as inferred from average ratings evolve over time

```{r libraries, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(fixest)
library(skimr)
library(infer)
library(modelsummary)
library(broom)
library(purrr)
library(viridis)
library(estimatr)
library(pdftools)
```

@@

## adding fixed effects
### titleType
We are observing behavior over time. But we are currently observing behavior for multiple types of behavior. Or more speicifally, for both movies AND series. But these are two different things. So while we still want to know the general genre prefference trends, we need to adjust for movie vs. series.

@@

If you compare these results against our skeleton model you may see that the standard errors have increased. This is good! this means our analysis has become a little more robust. But let's check our r-sqaured to be sure.

```{r echo=FALSE}
coeftable(simple_model)
```

```{r echo=FALSE}
coeftable(fixed_type_model)
```

@@

Last, because while out regression assumptions are mostly respected we still may want to increase the robustness of the coefficients. We do this by loosening these assumptions a little, given that hetroskedacity appears to be a little shady we loosen that assumption a little and then check the r sqaured again.

@@

coeftable(fixed_tth_model)
```

@@

```{r plotting results}
coefplot(fixed_tth_model)
```
As you can see from the plot some genres, such as romance, are largely significant are nicely consistent over the years. However, genres such as game-shows or news (which only rose after the 2000's) do not have observations for all years and the observations that are there are remarkably volatile given their large confidence intervals.

Next we want to see how a specific genre evolves over the years.

```{r}
list_of_coeficients <- coef(fixed_tth_model) %>%
  select(-id, -sample.var)

list_of_standard_deviations <- se(fixed_tth_model) %>%
  select(-id,-sample.var)

list_of_coeficients_long <- list_of_coeficients %>%
  pivot_longer(cols = -sample, names_to = "genre", values_to = "coef_value") %>%

# Pivot standard deviations longer
list_of_standard_deviations_long <- list_of_standard_deviations %>%
  pivot_longer(cols = -sample, names_to = "genre", values_to = "std_dev_value")

# Calculate p_threshold for each genre
graph_data <- left_join(list_of_coeficients_long, list_of_standard_deviations_long, by = "sample") %>%
  mutate(across(c(genre.x, genre.y), as.factor)) %>% 
  filter(genre.x == genre.y) %>%
  mutate(p_threshold = coef_value / std_dev_value,
         p_significance = ifelse(p_threshold > 1.96, 1, 0))

conf_level <- 0.95
z_value <- qnorm((1 + conf_level) / 2)

# Calculate confidence intervals
graph_data <- graph_data %>%
  mutate(
    lower_ci = coef_value - z_value * std_dev_value,
    upper_ci = coef_value + z_value * std_dev_value
  )

graph_data <- graph_data %>%
  drop_na()

# Plot with confidence intervals
ggplot(graph_data, aes(x = sample, y = coef_value, color = factor(p_significance))) +
  geom_point() +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2) +
  scale_color_manual(values = c("red", "green")) +
  xlab("Estimates") + ylab("Years") + facet_wrap(~genre.x) +
  scale_x_discrete(breaks = unique(graph_data$sample)[seq(1, length(unique(graph_data$sample)), length.out = 4)])
```

As you can see some genres are never significant, e.g., sports and thriller. While others become significant and never stop, e.g., history. There are also speaks in genres like war, where it seems to be falling in and out of favor. 
```{r}
